---
title: "Getting and Cleaning Data Quiz 1"
author: "Francisco Martín"
date: "September, 2018"
output: html_document
---


## 1.-
The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here: https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv and load the data into R. The code book, describing the variable names is here: https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FPUMSDataDict06.pdf. How many properties are worth $1,000,000 or more?

- 53   (Correct)

- 164

- 25

- 2076

Solution ->

``` {r prove_1}
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06hid.csv"
path <- file.path(getwd(),"dataQuestion1.csv")
if(!file.exists(path)){
        download.file(url,path)
}

data <- read.csv(path)
# VAL equal 24 means value is more than 1M$
length(which(data$VAL==24))
```

## 2.-

Use the data you loaded from Question 1. Consider the variable FES in the code book. Which of the "tidy data" principles does this variable violate?

- Each variable in a tidy data set has been transformed to be interpretable.

- Each tidy data table contains information about only one type of observation.

- Tidy data has one variable per column.  (Correct)

- Tidy data has one observation per row.

Solution -> FES has more than one variable in the column.


## 3.- 

Download the Excel spreadsheet on Natural Gas Aquisition Program here: https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx.

Read rows 18-23 and columns 7-15 into R and assign the result to a variable called: `dat`. What is the value of:
`sum(dat$Zip*dat$Ext,na.rm=T)`. (original data source: http://catalog.data.gov/dataset/natural-gas-acquisition-program)

- 36534720  (Correct)

- 0

- 154339

- NA

Solution ->

``` {r prove_3}
suppressPackageStartupMessages(library(xlsx))
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2FDATA.gov_NGAP.xlsx"
path <- file.path(getwd(),"dataQuestion3.xlsx")
if(!file.exists(path)){
        download.file(url,path)
}
colIndex <- 7:15 
rowIndex <- 18:23
dat <- read.xlsx(path,sheetIndex=1, colIndex = colIndex, rowIndex = rowIndex)
sum(dat$Zip*dat$Ext,na.rm=T)
```

## 4.-

Read the XML data on Baltimore restaurants from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml

How many restaurants have zipcode 21231?

- 28

- 100

- 127  (Correct)

- 130

Solution ->

``` {r prove_4}
suppressPackageStartupMessages(library("XML"))
url <- "http://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Frestaurants.xml"
doc <- xmlInternalTreeParse(url)
rootNode <- xmlRoot(doc)
zipcode <- xpathSApply(rootNode, "//zipcode", xmlValue)
table(zipcode == 21231)
```

## 5.-

The American Community Survey distributes downloadable data about United States communities. Download the 2006 microdata survey about housing for the state of Idaho using download.file() from here:

https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv

using the fread() command load the data into an R object `DT`. The following are ways to calculate the average value of the variable `pwgtp15` broken down by sex. Using the data.table package, which will deliver the fastest user time?


- mean(DT$pwgtp15,by=DT$SEX)

- mean(DT[DT$SEX==1,]$pwgtp15); mean(DT[DT$SEX==2,]$pwgtp15)

- sapply(split(DT$pwgtp15,DT$SEX),mean)

- tapply(DT$pwgtp15,DT$SEX,mean)

- DT[,mean(pwgtp15),by=SEX]  (Correct)

- rowMeans(DT)[DT$SEX==1]; rowMeans(DT)[DT$SEX==2]

Solution ->

``` {r prove_5}
suppressPackageStartupMessages(library(data.table))
url <- "https://d396qusza40orc.cloudfront.net/getdata%2Fdata%2Fss06pid.csv"
path <- file.path(getwd(),"dataQuestion5.csv")
if(!file.exists(path)){
        download.file(url,path)
}

DT <- fread(path)

system.time(DT[,mean(pwgtp15),by=SEX])
```
